---
title: "Correlation and Association"
author: "Statsomat.com"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
bibliography: ["references.bib"]
fontsize: 11pt
params:
  data: NA
  filename: NA
  fencoding: NA
  decimal: NA
  enc_guessed: NA
  vars1: NA
  vars2: NA
header-includes:
   - \usepackage{xcolor}
   - \setmainfont[BoldFont=FiraSans-Bold, Extension=.otf]{FiraSans-Regular}
   - \usepackage{booktabs}
   - \usepackage{longtable}
---


**Warning: In this app we evaluate only continuous vs. continuous variables. The automatic computation and interpretation delivered by the Statsomat should not completely replace the classical, made by humans graphical exploratory data analysis and statistical analysis. There may be data cases for which the Statsomat does not deliver the most optimal solution.**


```{r child = 'report_kernel.Rmd'}
```


```{r, results="asis"}
# Title 
tryCatch({
  
  if (sum(rateunique_df) >= 2L & nrow(df_num)>=5){
    cat("\n# References", fill=TRUE)
  }
  
}, error=function(e) {cat("")}

)
```



